What do incoming university students believe about open science practices in

### 2021-02-09 analysis/Manuscript.Rmd
update preprocessing & data import

# I fell down a massive git hub hole, so I'll make progress on this tomorrow!

@@

df$eligibility <- factor(df$eligibility)
df$eligibility_lab <- factor(df$eligibility_lab)

@@

>>>>

# all participants
n <- nrow(df)

@@

@@

Of those who started the survey (*n* = `r n`), `r el[5,2]` were eligible based on starting 
their first unit of study in psychology at a university within the next month.

<!-- [[ Breadcrumbs: work through the eligibility criteria from the prereg ]] -->
